\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-20 icse/eval.tex
Updated images in evaluation
Changed tag

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.23\textwidth}
    \includegraphics[width=\textwidth]{img/all-version-syntax.png}
    \caption{The parser generator.}
    \label{fig:syntax-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.23\textwidth}
    \includegraphics[width=\textwidth]{img/all-version-sem.png}
    \caption{The algorithm compiler.}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \caption{The result of the parser generator and the algorithm compiler for
  ECMAScript specifications from 2016 to 2020.}
  \label{fig:all-version}
\end{figure}

@@

To evaluate that \( \tool \) correctly extracts semantics, we extract semantics of ECMAScript
2020 via our tool. Above automatically extracted parts of semantics, we manually implement
\inred{XX} \( \ires \) functions for abstract algorithms failed to be automatically compiled.
Moreover, we fill in global setting based on ECMAScript 2020 specification as described
in Section~\ref{sec:framework}. The ECMAScript 2020 version is actively updated in
GitHub~\cite{es2020} to be released in the next year. Ecma Technical Committee 39 (TC39)
officially provides the conformance test suite, test262, for ECMAScript 2020.
Thus, we decide to evaluate the correctness of our syntax and semantics based on the test262.
However, the test262 also provides tests for in-progress features and other extensions
such as web browsers and internationalisation. Thus, we exclude them from our target tests.
Figure~\ref{table:test262} describes how to break down tests and the test results of extracted
semantics. We use test262 written in \inred{August 6, 2019}. In that version,
test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
for extensions and in-progres features. Then, we remove tests for non-strict mode because
we focus on only JavaScript codes in strict mode
as described in Section~\ref{sec:framework}. Finally, we remove the \inred{XXXX} tests
for not supported language features such as \inred{modules, JSON, RegExp, or Date}.
We test our extracted semantics for \inred{XXXXX} applicable tests and pass \inred{XXXX} tests.
There are several reasons of test failures; \inred{...}.

@@

\inred{- completion records??}
% The last issue is about the \textit{completion record type}, which is one of controversial features
% in ECMAScript specifications. They are used to describe the propagation of control
% flows and values in abstract algorithms. They are implicitly constructed
% in steps that return values that are not completion records in runtime semantics.
% Moreover, 
% It confuses the type of return values

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \[
      \begin{array}{c|r|r|r|r|r}
        \hline
        \text{version}
        & \multicolumn{1}{c|}{2016}
        & \multicolumn{1}{c|}{2017}
        & \multicolumn{1}{c|}{2018}
        & \multicolumn{1}{c|}{2019}
        & \multicolumn{1}{c}{2020}\\\hline
        \text{\#prods}
        & \text{\inred{XXX}}
        & \text{\inred{XXX}}
        & \text{\inred{XXX}}
        & \text{\inred{XXX}}
        & \text{\inred{XXX}}\\\hline
        \Delta
        & \multicolumn{1}{c|}{\text{-}}
        & \text{\inred{XXX}}
        & \text{\inred{XXX}}
        & \text{\inred{XXX}}
        & \text{\inred{XXX}}\\\hline
      \end{array}
    \]
    \caption{The parser generator.}
    \label{fig:syntax-all-version}
  \end{subfigure}
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\textwidth]{img/all-version-sem.png}
    \caption{The algorithm compiler.}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \caption{The result of the parser generator and the algorithm compiler for
  ECMAScript specifications from 2016 to 2020.}
  \label{fig:all-version}
\end{figure}

@@

To evaluate that \( \tool \) correctly extracts semantics, we extract semantics of ECMAScript
2020 via our tool. Above automatically extracted parts of semantics, we manually implement
\inred{XX} \( \ires \) functions for abstract algorithms failed to be automatically compiled.
Moreover, we fill in global setting based on ECMAScript 2020 specification as described
in Section~\ref{sec:impl}. The ECMAScript 2020 version is actively updated in
GitHub~\cite{es2020} to be released in the next year. Ecma Technical Committee 39 (TC39)
officially provides the conformance test suite, test262, for ECMAScript 2020.
Thus, we decide to evaluate the correctness of our syntax and semantics based on the test262.
However, the test262 also provides tests for in-progress features and other extensions
such as web browsers and internationalisation. Thus, we exclude them from our target tests.
Figure~\ref{table:test262} describes how to break down tests and the test results of extracted
semantics. We use test262 written in \inred{August 6, 2019}. In that version,
test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
for extensions and in-progres features. Then, we remove tests for non-strict mode because
we focus on only JavaScript codes in strict mode
as described in Section~\ref{sec:impl}. Finally, we remove the \inred{XXXX} tests
for not supported language features such as \inred{modules, JSON, RegExp, or Date}.
We test our extracted semantics for \inred{XXXXX} applicable tests and pass \inred{XXXX} tests.
There are several reasons of test failures; \inred{...}.

@@

### 2019-08-20 icse/overview.tex
Changed tag

\textbf{Outline.}
In the remainder of this paper, we describe the detailed techniques of
\( \tool \).  We first formally define \( \bnfes \) and how to
automatically generate parsers from given \( \bnfes \) using lookahead
parsers (Section~\ref{sec:parser}).  Then, we explain how to compile
abstract algorithms with tagged tokens into \( \ires \) functions using
compile rules, and introduce a rule generation assistant to
easily construct compile rules (Section~\ref{sec:compiler}).  After
describing implementation details (Section~\ref{sec:framework}),
we evaluate the effectiveness of \( \tool \)
(Section~\ref{sec:eval}), discuss related work
(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclude}).

>>>>

\textbf{Outline.}
In the remainder of this paper, we describe the detailed techniques of
\( \tool \).  We first formally define \( \bnfes \) and how to
automatically generate parsers from given \( \bnfes \) using lookahead
parsers (Section~\ref{sec:parser}).  Then, we explain how to compile
abstract algorithms with tagged tokens into \( \ires \) functions using
compile rules, and introduce a rule generation assistant to
easily construct compile rules (Section~\ref{sec:compiler}).  After
describing implementation details (Section~\ref{sec:impl}),
we evaluate the effectiveness of \( \tool \)
(Section~\ref{sec:eval}), discuss related work
(Section~\ref{sec:related}), and conclude (Section~\ref{sec:conclude}).
